### 2012-02-01 docs/compilers/compilers.tex
fix sectioning
add Hopper OpenMP note

\section{Compilers}

@@

%-----------------------------------------------------------------------------
\subsection{Cray}

@@

%-----------------------------------------------------------------------------
\subsection{gfortran}

@@

%-----------------------------------------------------------------------------
\subsection{IBM (xl* compilers)}

@@

%-----------------------------------------------------------------------------
\subsection{Intel}

@@

%-----------------------------------------------------------------------------
\subsection{PathScale}

@@

%-----------------------------------------------------------------------------
\subsection{PGI}

>>>>

@@

%-----------------------------------------------------------------------------
\section{Cray}

@@

%-----------------------------------------------------------------------------
\section{gfortran}

@@

%-----------------------------------------------------------------------------
\section{IBM (xl* compilers)}

@@

%-----------------------------------------------------------------------------
\section{Intel}

@@

Machine specific notes:

\begin{itemize}
\item on Hopper, with OpenMP:

From NERSC support ``Intel OpenMP has an extra thread at run time
beyond OpenMP threads.  This messes up the default affinity settings
for aprun, since you have a spare thread waiting until all the other
ones are completed.  You need to break the default affinity by adding
either one of these arguments to aprun:''

{\tt -cc none} or {\tt -cc numa\_node}.
\end{itemize}

%-----------------------------------------------------------------------------
\section{PathScale}

@@

%-----------------------------------------------------------------------------
\section{PGI}
